\section{Priors and normalization}

In this section we will add the priors in the parameter and normalize the data to see how it can improve the result on the trained methods.

The priors are for opencv argement given to the training model to specify the classes repartition within the data, here 84\% of non ad and 16\% of ads.

Normalizing the data can improve results depending on the method used. For instance for the svm it helps improving the results by "giving the same improtance to each point in the data vector". Meaning no value will be overpowerful over the others (range from -30 to 30 aginst range from -1 to 1).

\subsection{SVM}

Here we still use the autotrain method but only with


\subsubsection{linear}

The first type of model used was the linear one. The stopping criteria was of either a 100000 iterations or 1 for epsilon.

Results :
\begin{itemize}
  \item Correct classification : 91.78\%;
  \item Wrong classification : 8.22\%;
  \item False positive non ad : 7.08\%;
  \item False positive ad : 1.13\%.
\end{itemize}

Training the SVM (in progress) ..... (SVM 'grid search' => may take some time!)
Using optimal parameters degree 0.000000, gamma 1.000000, ceof0 0.000000
	 C 0.100000, nu 0.000000, p 0.000000
 Training ...... Done
Number of support vectors for trained SVM = 1

\subsubsection{Polynomial}

For this one, the number of itertion was reduced to 1000 because it was taking too much time.

Results :
\begin{itemize}
  \item Correct classification : 90.37\%;
  \item Wrong classification : 9.63\%;
  \item False positive non ad : 8.22\%;
  \item False positive ad : 1.42\%.
\end{itemize}
Using optimal parameters degree 0.490000, gamma 0.506250, ceof0 274.400000
	 C 2.500000, nu 0.000000, p 0.000000
 Training ...... Done
Number of support vectors for trained SVM = 189

\subsubsection{Radial Basis Function}

Since the result on the first model were not good enough I tried an other one, the polynomial one. As shown after the results were much better.

Results :
\begin{itemize}
  \item Correct classification : 91.2181\%;
  \item Wrong classification : 8.78187\%;
  \item False positive non ad : 7.93\%;
  \item False positive ad : 0.85\%.
\end{itemize}
Using optimal parameters degree 0.000000, gamma 0.000150, ceof0 0.000000
	 C 62.500000, nu 0.000000, p 0.000000
 Training ...... Done
Number of support vectors for trained SVM = 416


\subsubsection{Sigmoid}

Since the result on the first model were not good enough I tried an other one, the polynomial one. As shown after the results were much better.

Results :
\begin{itemize}
  \item Correct classification : 83.85\%;
  \item Wrong classification : 16.15\%;
  \item False positive non ad : 16.15\%;
  \item False positive ad : 0\%.
\end{itemize}
Training the SVM (in progress) ..... (SVM 'grid search' => may take some time!)
Using optimal parameters degree 0.000000, gamma 0.000010, ceof0 0.100000
	 C 0.100000, nu 0.000000, p 0.000000
 Training ...... Done
Number of support vectors for trained SVM = 382

\subsection{Neural Network}
For the neural network, the layers used are as follow :
  \begin{itemize}
    \item input layer, 1558, the number of point in the vector inputs;
    \item output layer, 2 outputs the number of class;
    \item hidden layer;
  \end{itemize}
  There will be no optimization on the number of cells used within the hidden layer and the number selected is of 40.

  Results :
  \begin{itemize}
    \item Correct classification : 92.92\%;
    \item Wrong classification : 7.08\%;
    \item False positive non ad : 4.25\%;
    \item False positive ad : 2.83\%.
  \end{itemize}
  7.08215
  7.08215
  models/NNPriRan.xml
  80

\subsection{Random forest}
The parameters used for the random forest are the following :
  \begin{itemize}
    \item number of variable randomly selected sqrt(n) (usually the best number);
  \end{itemize}
Results :
\begin{itemize}
  \item Correct classification : 93.2\%;
  \item Wrong classification : 6.80\%;
  \item False positive non ad : 5.95\%;
  \item False positive ad : 0.85\%.
\end{itemize}

Results on the testing database: data/ad\_cranfieldSub.test
	Correct classification: 330 (93.4844%)
	Wrong classifications: 23 (6.51558%)
	Class (digit 0) false postives 	21 (5.94901%)
	Class (digit 1) false postives 	2 (0.566572%)
7.36544
6.51558
models/RFPriRan.xml
818
